Categorical Predictor Embeddings in Actuarial Modeling

### 2021-04-04 manuscript/manuscript.Rmd
more fixes

Table: (\#tab:embeddings-occupancy-type) Learned embeddings for `occupancy_type`.

@@

Table: (\#tab:embeddings-flood-zone) Excerpt of learned embeddings for `flood_zone`.

@@

Although in this particular example we incorporate one-dimensional embeddings, one can easily include multidimensional
embeddings, which would increase the model's flexibility. The modeler would need to balance the additional lift with
some loss of interpretability, since with one-dimensional embeddings, our GLM structure dictates that there is a 
monotonic relationship between the predicted response and the input embedding, which could be desirable in certain
use cases (and undesirable in others.)

@@

Table: (\#tab:glm2) Coefficients of Model 3.

@@

Model 4 is architecturally identical to Model 2, with the only difference being the number of embedding dimensions:
instead of mapping factor levels to real numbers, we map them to points in Euclidean space, where the dimension of the 
space is the ceiling
of the factor's cardinality divided by two. Formally, in the notation of Section \ref{catdata},
$q_{\mathcal{P}^j}=\ceil{n^j_{\mathcal{P}}/2}$ for variable $X_j$. Following the practice from the previous three
models, we list the fitted embeddings for a couple variables in Tables \@ref(tab:nn2-occupancy-type) and 
\@ref(tab:nn2-flood-zone). Note that, for `flood_zone`, we are
only displaying the embedding for *one* level.

>>>>

Table: (\#tab:embeddings-occupancy-type) Learned embeddings for `occupancy_type` in Model 2.

@@

Table: (\#tab:embeddings-flood-zone) Excerpt of learned embeddings for `flood_zone` in Model 2.

@@

Although, in this particular example, we incorporate one-dimensional embeddings, one can easily include multidimensional
embeddings, which would increase the model's flexibility. The modeler would need to balance the potential 
additional lift with overfitting and
some loss of interpretability, since, with one-dimensional embeddings, our GLM structure dictates that there is a 
monotonic relationship between the predicted response and the input embedding, which could be desirable in certain
use cases (and undesirable in others.)

@@

Table: (\#tab:glm2) Fitted coefficients of Model 3.

@@

Model 4 is architecturally identical to Model 2, with the only difference being the number of embedding dimensions:
instead of mapping factor levels to real numbers, we map them to points in Euclidean space, where the dimension of the 
space is the ceiling
of the factor's cardinality divided by two. Formally, in the notation of Section \ref{catdata},
$q_{\mathcal{P}^j}=\ceil{n^j_{\mathcal{P}}/2}$ for variable $X_j$. Following the discussion thus far, we list the
 learned embeddings for a couple variables in Tables \@ref(tab:nn2-occupancy-type) and 
\@ref(tab:nn2-flood-zone). Note that, for `flood_zone`, we are
only displaying the embedding for *one* level.
